% !TEX TS-program = xelatex
% !TEX encoding = UTF-8 Unicode
% -*- coding: UTF-8; -*-
% vim: set fenc=utf-8

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% CV.tex
%% <https://github.com/zachscrivena/simple-resume-cv>
%% This is free and unencumbered software released into the
%% public domain; see <http://unlicense.org> for details.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% See "README.md" for instructions on compiling this document.

\documentclass[a4paper,MMMyyyy,nonstopmode]{simpleresumecv}
% Class options:
% a4paper, letterpaper, nonstopmode, draftmode
% MMMyyyy, ddMMMyyyy, MMMMyyyy, ddMMMMyyyy, yyyyMMdd, yyyyMM, yyyy

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% PREAMBLE.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% CV Info (to be customized).
\newcommand{\CVAuthor}{Xingfan Xia}
\newcommand{\CVTitle}{Xingfan's CV}
\newcommand{\CVNote}{CV compiled on {\today}}
\newcommand{\CVWebpage}{https://xiax.xyz}

% PDF settings and properties.
\hypersetup{
pdftitle={\CVTitle},
pdfauthor={\CVAuthor},
pdfsubject={\CVWebpage},
pdfcreator={XeLaTeX},
pdfproducer={},
pdfkeywords={},
unicode=true,
bookmarks=true,
bookmarksopen=true,
pdfstartview=FitH,
pdfpagelayout=OneColumn,
pdfpagemode=UseOutlines,
hidelinks,
breaklinks}

% Shorthand.
\newcommand{\Code}[1]{\mbox{\textbf{#1}}}
\newcommand{\CodeCommand}[1]{\mbox{\textbf{\textbackslash{#1}}}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% ACTUAL DOCUMENT.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\pagestyle{empty}
\begin{document}

%%%%%%%%%%%%%%%
% TITLE BLOCK %
%%%%%%%%%%%%%%%

\Title{\CVAuthor}

\begin{SubTitle}
\href{https://www.google.com/maps/place/8502+134th+Ct+NE,+Redmond,+WA+98052}
{8502 134th Ct NE, Redmond, WA 98052}
\par
\href{mailto:xingfanxia@gmail.com}
{xingfanxia@gmail.com}
\,\SubBulletSymbol\,
+1\,(507)\,403-1689
\,\SubBulletSymbol\,
\href{\CVWebpage}
{\url{\CVWebpage}}
\end{SubTitle}

\begin{Body}
%%%%%%%%%%%%%%%%%%%%%
%% WORK EXPERIENCE %%
%%%%%%%%%%%%%%%%%%%%%

\Section
{Work\newline
Experience}
{Work Experience}
{PDF:WorkExperience}

\Entry
\href{https://computelabs.com/}
{\textbf{Compute Labs}},
Remote, Redmond, WA

\Gap
\BulletItem
Co-Founder and Chief Technology Officer
\hfill
\DatestampYM{2024}{8} --
Present
\begin{Detail}
\SubBulletItem
\textbf{Leading the technological vision for democratizing AI compute access through blockchain-based tokenization, building the financial ecosystem for compute as an emerging asset class.}
\SubBulletItem
Architecting the Compute Tokenization Protocol (CTP) that transforms physical GPUs (H100s, B200s) into tradeable digital assets, enabling fractional ownership and enhanced liquidity in AI infrastructure investments.
\SubBulletItem
Directing R\&D teams in developing the AI-Fi ecosystem that merges advanced AI infrastructure with DeFi protocols, creating innovative financial instruments and structured products for AI compute investments.
\SubBulletItem
Spearheading the development of GNFT \& COMPUTE token systems, implementing multi-faceted validation and benchmarking frameworks to ensure transparent, verifiable, and secure GPU tokenization transactions.
\SubBulletItem
Building scalable blockchain infrastructure to optimize GPU utilization across decentralized and centralized compute networks, maximizing returns for investors throughout the AGI development journey.
\end{Detail}

\BigGap
\Entry
\href{https://aws.amazon.com/athena/}
{\textbf{Amazon Web Service -- Athena}},
Redmond, WA

\Gap
\BulletItem
Software Engineer - AI/ML Infrastructure
\hfill
\DatestampYM{2022}{4} --
\DatestampYM{2024}{6}
\begin{Detail}
\SubBulletItem
\textbf{Building next-generation data infrastructure optimized for AI/ML workloads, enabling large-scale machine learning analytics on petabyte-scale datasets.}
\SubBulletItem \textbf{Tech Stack: Java, Python, Apache Spark, Apache Iceberg, AWS ML Services, Distributed Computing}
\SubBulletItem
Architected CTAS feature for Iceberg Tables enabling efficient ML data preprocessing. Released at AWS RE:INVENT 2022 with millions of ML-focused queries executed since launch.
\SubBulletItem
Optimized Hive JSON Serde library for ML data ingestion, improving feature extraction performance by 30\% and reducing ML pipeline failures by 60\%.
\SubBulletItem
Developed virtualized table connector for ML feature stores, improving AI application data accessibility by 40\% and projected to save \$4M annually in ML infrastructure costs.
\end{Detail}

\BigGap
\Entry
\href{https://www.apple.com/}
{\textbf{Apple}},
Cupertino, CA

\Gap
\BulletItem
Machine Learning Engineer - Siri Intelligence
\hfill
\DatestampYM{2020}{8} --
\DatestampYM{2022}{4}
\begin{Detail}
\SubBulletItem
\textbf{Developing advanced AI systems and machine learning models to enhance Siri's intelligence across iOS, macOS, watchOS, and tvOS platforms.}
\SubBulletItem \textbf{Tech Stack: Python, Objective-C, TensorFlow, PyTorch, MLOps, Apache Spark, Real-time ML Inference}
\SubBulletItem
Designed on-device ML framework for user profiling using deep learning algorithms, serving as core intelligence layer for Apple Maps and Apple News recommendation systems.
\SubBulletItem
Built automated MLOps pipeline for continuous model training with A/B testing framework and automated performance monitoring, reducing manual ML engineering overhead by 40\%.
\SubBulletItem
Developed contextual AI prediction service using ensemble learning to anticipate user intent, powering Siri Shortcuts and proactive recommendations.
\end{Detail}

\BigGap
\Entry
\href{https://press.airbnb.com/about-us/}
{\textbf{Airbnb}},
San Francisco, CA

\Gap
\BulletItem
Machine Learning Engineer - Trust \& Safety AI
\hfill
\DatestampYM{2019}{1} --
\DatestampYM{2020}{8}
\begin{Detail}
\SubBulletItem
\textbf{Building AI-powered fraud detection and trust \& safety systems using advanced machine learning techniques and real-time inference engines.}
\SubBulletItem \textbf{Tech Stack: Python, Java, Scala, TensorFlow, XGBoost, MLflow, Apache Kafka, Real-time ML Serving}
\SubBulletItem
Developed ML algorithms for fake review detection using NLP and anomaly detection, reducing fraudulent reviews to 1\% of peak volume and preventing \$2M in losses.
\SubBulletItem
Implemented ensemble learning for comprehensive user risk scoring system, combining multiple ML models to evaluate host and guest trustworthiness.
\SubBulletItem
Deployed ML-driven policy engine for automated risk-based payout delays, preventing 60\% of fraudulent payouts and generating \$10M in annual savings.
\SubBulletItem
Architected real-time ML serving infrastructure providing low-latency risk signals through Kafka streams and Redis caching for sub-100ms inference.
\end{Detail}

% \BigGap
% \Entry
% \href{https://lino.network/}
% {\textbf{Lino Network}},
% Cupertino, CA

% \Gap
% \BulletItem
% Founding Engineer
% \hfill
% \DatestampYM{2018}{03} --
% \DatestampYM{2018}{10}

% % \newline
% % Building a decentralized video and live streaming platform.
% \begin{Detail}
% \SubBulletItem \textbf{Building a decentralized video and live streaming platform -- Dlive.}
% \SubBulletItem \textbf{Tech Stack: Python, Golang, Javascript, VueJS, Splunk, ELK, AWS(S3, Kinesis, Lambda, Route53, etc)}
% \SubBulletItem 
% Built Dlive's front-end website, video transcoding/storage/distribution service, and metrics data pipeline from scratch.
% \SubBulletItem
% Secured \$20 million in funding through a private token sale led by ZhenFund and exited selling Dlive to BitTorrent.
% \end{Detail}

% \BigGap
% \Entry
% \href{https://hq.vevo.com/}
% {\textbf{Vevo LLC}},
% San Francisco, CA

% \Gap
% \BulletItem
% Software Engineer Intern
% \hfill
% \DatestampYM{2017}{06} --
% \DatestampYM{2017}{09}
% \newline
% (Data \& Machine Learning Team)
% \begin{Detail}
% \SubBulletItem
% Designed and implemented a Q\&A chatbot using AWS Lambda, Python and AWS Lex. Deployed the chatbot on Facebook Messenger and Slack.
% \SubBulletItem
% Built a multi-seed recommendation engine. Deployed as an API service, a Web App, and a tvOS App as POC demos.
% \SubBulletItem
% Analyzed visuals of music videos, generated playlists based on similar visual elements grouped by LDA topic modeling.
% \SubBulletItem
% Deployed a Jupyterhub system on an AWS P2 instance to facilitate team's research and exploratory works related to machine learning and deep learning. Typically made model training 6 times faster.
% \end{Detail}

%%%%%%%%%%%%%%
%% Projects %%
%%%%%%%%%%%%%%

% \Section
% {Projects}
% {Projects}
% {PDF:Projects}

% \Entry
% \href{https://github.com/xingfanxia/comps_ediscovery}
% {\textbf{Tree Discovery}}
% % \newline
% % (An implementation of the Random Forest Algorithm)
% \Gap
% \BulletItem
% Lead
% \hfill
% \DatestampYM{2017}{10} --
% \DatestampYM{2018}{05}

% \begin{Detail}
% \SubBulletItem
% Implemented the Random Forest Algorithm from scratch in Python with a team of 6.
% \SubBulletItem
% Processed the raw and messy ENRON email dataset into a usable training set and test set with TF-IDF, DB-SCAN, and LSA topic aggregation.
% % \SubBulletItem
% % Reduced the training speed of a typical tree from 2 minutes down to less than 10 seconds.
% \SubBulletItem
% Tested the performance of the implementation against the ENRON dataset, our F1 Score is comparable to the results presented at TREC Conference 2011.
% \SubBulletItem
% Designed and built a demo e-discovery product that utilizes the idea of semi-supervised learning, allow users to tag relevant documents as training set in each iteration of predictions to continuously improve the model's accuracy and recall.
% \end{Detail}

% \BigGap
% \Entry
% \href{https://github.com/mahu-search}
% {\textbf{Mahu}}

% \Gap
% \BulletItem
% Contributor
% \hfill
% \DatestampYM{2017}{07} --
% \DatestampYM{2018}{03}

% \begin{Detail}
% \SubBulletItem
% Built a web app with VueJS and bulma that allows developers from China to perform searches related to coding and the app will crawl aggregate results from sites like StackOverflow, SuperUser, Stack Exchange, etc. 
% \SubBulletItem
% Integrated various translation API avialble to empower users who are not proficient with English.
% \end{Detail}

% \BigGap

% \Entry
% \href{https://moegirl.org/Mainpage}
% {\textbf{Moegirl Wiki}}
% \newline
% (Open Source Wiki Based on MediaWiki)
% \Gap
% \BulletItem
% Contributor
% \hfill
% \DatestampYM{2016}{03} --
% \DatestampYM{2018}{03}
% \begin{Detail}
% \SubBulletItem
% Worked with a team of about 20 contributors to maintain day-to-day running of the Wiki.
% \SubBulletItem
% Prototyped a redesign of the main page of the iOS app with the lead iOS developer.
% \end{Detail}

% \BigGap
% \Entry
% \href{https://steamcommunity.com/sharedfiles/filedetails/?id=440115357}
% {\textbf{Dota IMBA}}
% \newline
% (Custom Game Based on Popular Online Multiplayer Game Dota2 with Six Million Subscribers)

% \Gap
% \BulletItem
% Contributor
% \hfill
% \DatestampYM{2017}{07} --
% \DatestampYM{2018}{03}
% \begin{Detail}
% \SubBulletItem
% Applied patches for community reported bug and adjust parameters for better balance.
% \SubBulletItem
% Communicated with active players on discord channels to collect critiques and ideas for improvement.
% \end{Detail}


% \BigGap
% \Entry
% \href{https://github.com/xxf1995/VRGame}
% {\textbf{Zombie Forest}}

% \Gap
% \BulletItem
% Contributor
% \hfill
% \DatestampYM{2016}{6} --
% \DatestampYM{2016}{6} --
% \begin{Detail}
% \SubBulletItem
% Learned basics of Unity and Oculus SDK and built the game from scratch in 36 hours at CarlHack 2016.
% \SubBulletItem
% Designed the basic gameplay and AI logic, implemented how player character interact with the map.
% \end{Detail}

%%%%%%%%%%%%%%%
%% EDUCATION %%
%%%%%%%%%%%%%%%

\Section
{Education}
{Education}
{PDF:Education}

\Entry
\href{https://www.carleton.edu/}
{\textbf{Carleton College}},
Northfield, Minnesota

\Gap
\BulletItem
B.A. in
\href{https://apps.carleton.edu/curricular/cs/}
{Computer Science}
\hfill
Graduated \DatestampYM{2018}{06}

%%%%%%%%%%%%%%%%%%%%%
%%Technical SKILLS %%
%%%%%%%%%%%%%%%%%%%%%

\Section
{Technical Skills}
{Technical Skills}
{PDF:Technical Skills}

\BulletItem
Programming Languages: Proficiency in Python, Java, Golang, Javascript, Scala, Objective-C

\Gap
\BulletItem
Experienced AWS Services: Athena, S3, SQS, EC2, Lambda, API Gateway, Auto Scaling Group, Cloudfront, Route 53, CodePipeline, CodeBuild, CodeDeploy, Kinesis

\Gap
\BulletItem
Data Engineering \& Analysis: Data Analysis Libraries, OpenCV, Visualization Tools, Scipy, Numpy, Pandas, ELK, Apache Iceberg, Apache Spark, Apache Kafka, Airflow
\let\clearpage\relax

\end{Body}
\end{document}
